Transforming Trash as an Artistic Act

### 2016-01-17 chapter4_final.tex
turnitin fixes
Former-commit-id: c4e9dd913032a23d4355c7f057bba5be233580f1

\begin{singlespace}
% FROM Wild Art. quote taken from the television series `American Masters', Season 5, Episode 8, John Cage: I have nothing to say and I am saying it (aired on 17 September 1990).
\epigraph{The first question I ask myself when something doesn't seem to be beautiful is why do I think it's not beautiful? And very shortly you discover that there is no reason. If we can conquer that dislike, or begin to like what we did dislike, then the world is more open. That path ---of increasing one's enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}, 2013}
\end{singlespace}

@@

%
%
% TODO: Be careful on tenses.
\section{The Statement}
Refuse is part of people’s consumption practices. It is a very common concept from developed cities to rural areas, from modern societies to ancient societies. It is not wanted, thrown away, kept away. It is considered as useless, disgusting, abject, unattractive, and harmful to the people and nature. Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man's trash is another man's treasure}.

@@

% [SODA CAPS]
I remember from my childhood that we were collecting soda caps and were playing with them. We were looking everywhere to collect them. Some caps were found less and they worth more in the game. We put them on the railways to make them flat. After the train had passed we had perfect flat caps for our games. At that time, it was not waste for us. It has a value and part of our games and indispensable source of fun. The notion of playing with it can be related with the Picasso's collage work \quotes{Still Life with Chair Caning} mentioned previously. He pasted letters of the French word \quotes{JOU} means \quotes{game} signifying that playing with the materials. We were already playing with trash while we were child. Therefore, it can be better understand that why Picasso said that \quotes{every child is an artist}.

% [VASVIYE HOCA]
Another important memory is from my primary school teacher. When I was at third class, our teacher wanted us to bring colorful papers to make something (whatever it is I do not remember now). The day after we brought some colorful paper that was bought from stationery store. Our papers' shape and color looked same. However her papers were different in every dimension. They were cut out from packages and advertisements. I remember clearly that she suggested that same for us. \quotes{Do not throw out packages, look for the useful parts and keep them to use later.} Whenever I am going to throw something away, this comes to my mind. Can it be reused? Every time it is not obvious that how can it be useful, but at some point it becomes an indispensable practice. Further, this practice is also support to the bricolage methodology. Keeping many things makes easier to build (or produce) whatever at hand.

% [Song Dong]
The main idea is to save them to use later. For some people it is a life saving practice. It can be seen in the case of artist Song Dong's mother (mentioned in chapter 2). This practice result in establishing stronger and intimate relationship with objects.

I am very uncomfortable with the act of discarding. I often think that by discarding objects, I am missing their potentials. I must find another use which is more effective than throwing away. At least I can give them to someone else who can use it for own purposes. Seeing papers on the waste bin is a disappointment for me. As artist Aaron Kramer argues that \quotes{[t]rash is the failure of imagination} \citep[as cited in][]{meyer2007turning}. There is a lot of effort to produce objects and it seems that all this efforts are wasted. What I mention is not related about ultimate productivity. It is more close to being thoughtful, and taking responsibility of tools, items and objects that we are using. Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception. On the contrary, sometimes I became overwhelmed because of the significant amount of leftover from daily activities and in order to move on I need to leave them behind. It is the result of inevitable rhythm of modern life style. Consuming and wasting is part of people's daily routine and most of the time they are not aware of what they consume, and what they discard. In the scope of this thesis subject, saving objects rather them getting rid of them is an effective way of breaking the routines. The use of that object can be decided in the future.

% [encouraging point]
One of the encouraging factor of working on trash is to explore something different that others cannot see. In other words, it contains eureka moments. Because it is ignored by discarding and therefore undiscovered. It waits us to be discovered and possibly (as Picasso's explanation on his work 'Bull's Head'\footnote{See epigraph in the beginning of Chapter 3}) discovered again and again.

@@

% TODO Lars Eighner BIB'e eklenecek.

% NEW PART [collecting] 
\subsection{Collecting}
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that:

@@

% OWNER
\quotes{The question of who owns these discards is not trivial} \citep{zimring2012encyclopedia}. This question makes me feel uncomfortable because of thinking that stealing that someone elses' objects. Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory. You already know that it owned by somebody else and after a while owner can take them. I solved this issue checking the leaved papers in every couples hours. If it stays there I take them. Further I encountered that If nobody takes them for a long time servants collect them.

The issue of owner becomes more complicated when owners' social status considered. Zubiaurre mentions that no body cares her student scavenged through people’s trash in a poor neighborhood \citep[as cited in][]{pricano2011trashtalk}. On the contrary when the same student went to Beverly Hills home of the many actors and celebrities in California to scavenge nearly the police were called.

% CONTRIBUTIONS OF PEOPLE
As mentioned previously many people contributed to the project by collecting. Whenever I meet my friends I ask them to save their discard for the project. The importance of collaboration with them can be understood the term "citizen science" which is \quotes{defined as scientific research performed in part or in whole by volunteers who are not professional scientists} \citep{robson2012using}. I need to note that this is not a scientific project but the notion belongs there. The value of it lies in the collective intelligence of the contributors. In the scope of this thesis the term can be interpreted as people bring their own creativity and interpretation to the project by collecting the items that they reach and select. When the number of contributors are increased the diversity of the collected material will be increased and this will echoed in the notebooks.

@@

Collected items reflect my and contributors' consumption practices. People as mentioned previously consumption patterns can be tracked from their leftover. From logos of companies onto the packages reveal people's choices and give clues about their social status.

@@

\textbf{Burger King packages} are collected from the office where I work. At launch time, some of the colleagues order their meal from Burger King which is a global chain of fast food restaurant. Meals are delivered to the office with paper packages. The package of the meal is collected and used as a cover of notebooks.

Inside the bag one paper package is used for French fries which is oily and paper is very good to absorb oil. Some people think that it is disgusting to use it for other purposes because of oil onto it. But immediately I replied them \quotes{you just eat that oily fires so what is wrong with it?} At the same time what \cite[5]{strasser1999waste} said comes to my mind; \quotes{Nothing is inherently trash}. She refers to resolution on dirt of \cite[36]{douglas2003purity}:
\begin{quote}
Shoes are not dirty in themselves, but it is dirty to place them on the dining table; food is not dirty in itself but it is dirty to leave cooking utensils in the bedroom, or food bespattered on clothing; similarly bathroom equipment in the drawing room; clothing lying on chairs; out-door things in-doors; upstairs things downstairs; under-clothing appearing where over-clothing should be and so on.
\end{quote}

This simply explains that our perceptions to the objects are relative and change in their usage context.

% TODO relocate
%Trash is something that is out of sight, out of mind. Paid little attention to them and only catches attention when it is in wrong place. It is an unexpected object for people. Therefore transformation of it can create powerful and surprising effect onto the people.

%\paraphrase{Thompson comments that we only notice rubbish when it is in the wrong place, and highlights the embarrassment and anxiety that mis-placed rubbish, or rubbish which has found its way in to the wrong place can cause ‘Something which has been discarded, but never threatens to intrude, does not worry us at all.’ (1979: 92) but rubbish in the wrong place is ‘emphatically visible and extremely embarrassing’ (1972: 92). Rubbish objects are things that are no longer used or loved or cared for and often no longer seen. Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust. (Summary From Liz Parsons.)}

@@

\textbf{Varuna Gezgin papers} are the pages of obsolete dinner menu. When leaving there I showed my notebooks and asked to the cashier that I could able to present them at Varuna Gezgin. He immediately mentioned their vast amount of unused papers and gave me some of them that I can able to carry with me. This was a very strange experience for me because I did not expect such a thing. These paper are used inside of the notebooks as a page.

% I'm collecting the paper that are under the plates. When we are leaving this place, I ask the cashier at the desk that \quotes{I am making small notebooks and is it possible to exhibit there?} I asked that is it possible to give them to people. Firstly he asked me that did I sell them or not but I said \quotes{no they are free and part of my thesis project.} After that he offered me to give e are a lot of unused papers. I can give you. they are not used and waiting to be recycling. I took some of the papers, and that papers are part the sheets of these papers.

\textbf{The banner} is carried at graduation ceremony of Middle East Technical University in 2011 by the new Computer Engineering graduates. In Middle East Technical University there is a tradition that in graduation ceremony new grads walk through in the stadium and greet to the tribunes. With this event they carry some banners to express their feelings and point out the issues of the country in an ironic and humorous way. This one of them. At that time there are serious debates about freedom on the web. Most of the website are banned from the decision to the courts and they were not accessible. The slogan (Access to this banner is blocked by a court decision) decided by the new grads and before the ceremony I printed out the slogan to carried out as many people as it can and easy to readable from the people who seat at the tribunes.After the ceremony I could not throw away this banner. I do not know what to do it. It is a very big roll of paper to save but I could not throw away. I think that I will figure out later. Maybe I can use it as a draft paper. However is it worth to cut out this all long banner? Moreover to strengthen the banner we tape it from its boundaries. In other words some of the areas can not appropriate for writing. When I decided to my thesis subject I remembered to this banner. It stands in a corner in a dusty way. Now it is time to use it. It waited very log time and it is time to revive. I cut out them to the smaller pieces to use them as pages of notebooks. All pages have unique patterns. They contain parts of letters. Most of the time it is not recognizable belongs to which letter. These papers offers unique writing experience to the writer because of the patterns of letters and residue of tapes.

@@

Most of the materials that I collect are mass produced items. Generally their usage fall into the two category; education and food industry. They are found on public places. They are not personal objects like in the work of Tracey Emin's \quotes{My Bed} even if it can be claimed that the collected papers from the laboratory contains personal travel tickets. Identity of owner are not certain.

@@

There are different dimensions of notebooks. Most of them are half of A4 or quarter of it.

@@

\textbf{Reunion.} These notebook's pages are collected from restaurant Varuna Gezgin, in Ankara. We went there to meet some friends after long time. One of them was coming from Australia, the other one was coming from Norway. They were my friends from the university. We united again at this restaurant. The place has also similar story. Their founders and workers travel around the world. It is a popular restaurant of travelers. The decoration of that place contains a lot of items collected from different sides of the world. The concept of the place and our meeting perfectly matched. Same exist for the papers actually, they are separated from big paper rolls in the factory and by the action making notebooks they are also reunited again. These notebooks represent my memory about the place.

\textbf{Secondhand.} It can be thought that these notebooks are second hand objects. Used by someone else and still appropriate for reusing.

% TODO burada bir isim uydurmak gerekli.
\textbf{Daro.} For some of the notebooks it is not obvious to name them. At this point approach of Kurt Schwitters provides me a way. He generated his frequently used word \quotes{Merz} from an advertisement. It is a nonsense word and used in most of his works. I followed what he did and generated a word from the papers that used inside of the notebooks. I use the word \quotes{Daro} extracted from \quotes{Vardaroma Dondurmacısı} for the ones whose story are not obvious and significant.

@@

%
%
\subsection{Website}
Finding a new place to the discarded items is one of the main purposes of this project. Not only it finds a place in people's life again, but also it finds another place in the digital space.

@@

%SketchBook Project is also inspired me a lot especially in terms of website. This project provides a platform to people in order to share their works with other people. It contains lots of works from all over the world. Full of creativity and showcase of richness of people's expressions on the small notebooks. My work can be considered as a sketch book project through trash. Sketches or only creative progress is not the only consideration. You can send your lecture notes.

>>>>

\begin{singlespace}
\epigraph{The first question I ask myself when something doesn’t seem to be beautiful is why do I think it’s not beautiful? And very shortly you discover that there is no reason. If we can conquer that dislike, or begin to like what we did dislike, then the world is more open. That path ---of increasing one’s enjoyment of life--- is the path, I think, we all best take: to use art not as self-expression, but as self-alteration; to become more open.}{\hfill---John Cage, \textit{Wild Art}, 2013}
\end{singlespace}

@@

%
%
% TODO: Be careful on tenses.
\section{The Statement}
Refuse is part of people’s consumption practices. It is a very common concept from developed cities to rural areas, from modern societies to ancient societies. It is not wanted, thrown away, kept away. It is considered as useless, disgusting, abject, unattractive, and harmful to the people and nature. Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man’s trash is another man’s treasure}.

@@

% [SODA CAPS]
I remember from my childhood that we were collecting soda caps and were playing with them. We were looking everywhere to collect them. Some caps were found less and they worth more in the game. We put them on the railways to make them flat. After the train had passed we had perfect flat caps for our games. At that time, it was not waste for us. It has a value and part of our games and indispensable source of fun. The notion of playing with it can be related with the Picasso’s collage work \quotes{Still Life with Chair Caning} mentioned previously. He pasted letters of the French word \quotes{JOU} means \quotes{game} signifying that playing with the materials. We were already playing with trash while we were child. Therefore, it can be better understand that why Picasso said that \quotes{every child is an artist}.

% [VASVIYE HOCA]
Another important memory is from my primary school teacher. When I was at third class, our teacher wanted us to bring colorful papers to make something (whatever it is I do not remember now). The day after we brought some colorful paper that was bought from stationery store. Our papers’ shape and color looked same. However her papers were different in every dimension. They were cut out from packages and advertisements. I remember clearly that she suggested that same for us. \quotes{Do not throw out packages, look for the useful parts and keep them to use later.} Whenever I am going to throw something away, this comes to my mind. Can it be reused? Every time it is not obvious that how can it be useful, but at some point it becomes an indispensable practice. Further, this practice is also support to the bricolage methodology. Keeping many things makes easier to build (or produce) whatever at hand.

% [Song Dong]
The main idea is to save them to use later. For some people it is a life saving practice. It can be seen in the case of artist Song Dong’s mother (mentioned in chapter 2). This practice result in establishing stronger and intimate relationship with objects.

I am very uncomfortable with the act of discarding. I often think that by discarding objects, I am missing their potentials. I must find another use which is more effective than throwing away. At least I can give them to someone else who can use it for own purposes. Seeing papers on the waste bin is a disappointment for me. As artist Aaron Kramer argues that \quotes{[t]rash is the failure of imagination} \citep[as cited in][]{meyer2007turning}. There is a lot of effort to produce objects and it seems that all this efforts are wasted. What I mention is not related about ultimate productivity. It is more close to being thoughtful, and taking responsibility of tools, items and objects that we are using. Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception. On the contrary, sometimes I became overwhelmed because of the significant amount of leftover from daily activities and in order to move on I need to leave them behind. It is the result of inevitable rhythm of modern life style. Consuming and wasting is part of people’s daily routine and most of the time they are not aware of what they consume, and what they discard. In the scope of this thesis subject, saving objects rather them getting rid of them is an effective way of breaking the routines. The use of that object can be decided in the future.

% [encouraging point]
One of the encouraging factor of working on trash is to explore something different that others cannot see. In other words, it contains eureka moments. Because it is ignored by discarding and therefore undiscovered. It waits us to be discovered and possibly (as Picasso’s explanation on his work ’Bull’s Head’\footnote{See epigraph in the beginning of Chapter 3}) discovered again and again.

@@

% TODO Lars Eighner BIB’e eklenecek.

% NEW PART [collecting] 
\subsection{Collecting}
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner’s instructions helped me a lot when collecting objects. He writes that:

@@

% OWNER
\quotes{The question of who owns these discards is not trivial} \citep{zimring2012encyclopedia}. This question makes me feel uncomfortable because of thinking that stealing that someone elses’ objects. Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory. You already know that it owned by somebody else and after a while owner can take them. I solved this issue checking the leaved papers in every couples hours. If it stays there I take them. Further I encountered that If nobody takes them for a long time servants collect them.

The issue of owner becomes more complicated when owners’ social status considered. Zubiaurre mentions that no body cares her student scavenged through people’s trash in a poor neighborhood \citep[as cited in][]{pricano2011trashtalk}. On the contrary when the same student went to Beverly Hills home of the many actors and celebrities in California to scavenge nearly the police were called.

% CONTRIBUTIONS OF PEOPLE
As mentioned previously many people contributed to the project by collecting. Whenever I meet my friends I ask them to save their discard for the project. The importance of collaboration with them can be understood the term \quotes{citizen science} which is \quotes{defined as scientific research performed in part or in whole by volunteers who are not professional scientists} \citep{robson2012using}. I need to note that this is not a scientific project but the notion belongs there. The value of it lies in the collective intelligence of the contributors. In the scope of this thesis the term can be interpreted as people bring their own creativity and interpretation to the project by collecting the items that they reach and select. When the number of contributors are increased the diversity of the collected material will be increased and this will echoed in the notebooks.

@@

Collected items reflect my and contributors’ consumption practices. People as mentioned previously consumption patterns can be tracked from their leftover. From logos of companies onto the packages reveal people’s choices and give clues about their social status.

@@

\textbf{Burger King packages} (Figure \ref{fig:BurgerKingBag}) are collected from the office where I work. At launch time, some of the colleagues order their meal from Burger King which is a global chain of fast food restaurant. Meals are delivered to the office with paper packages. The package of the meal is collected and used as a cover of notebooks.

Inside the bag one paper package is used for French fries which is oily and paper is very good to absorb oil. Some people think that it is disgusting to use it for other purposes because of oil onto it. But immediately I replied them \quotes{you just eat that oily fires so what is wrong with it?} At the same time what \citet[5]{strasser1999waste} said comes to my mind; \quotes{Nothing is inherently trash}. She refers to resolution on dirt of \citet[36]{douglas2003purity}:

\begin{quote}
Shoes are not dirty in themselves, but it is dirty to place them on the dining table; food is not dirty in itself but it is dirty to leave cooking utensils in the bedroom, or food bespattered on clothing; similarly bathroom equipment in the drawing room; clothing lying on chairs; out-door things in-doors; upstairs things downstairs; under-clothing appearing where over-clothing should be and so on.
\end{quote}

This simply explains that our perceptions to the objects which are relative and change in their usage context. Further it signifies that trash only catches attention of people when it is in wrong place. \citet[92]{thompson1979rubbish} argues that people only recognize rubbish when it is in unusual place and condition. He also points out rubbish in the wrong place is \quotes{emphatically visible and extremely embarrassing.} \citet[391]{parsons2008thompsons} concludes that rubbish is \quotes{no longer used or loved or cared for and often no longer seen. Rubbish objects linger on the periphery of our lives, in the back of the drawer, bottom of the wardrobe or cupboard, corner of the garage or garden shed gathering dust.}

@@

\textbf{Varuna Gezgin papers} (Figure \ref{fig:VarunaGezgin}) are the pages of obsolete dinner menu. When leaving there I showed my notebooks and asked to the cashier that I could able to present them at Varuna Gezgin. He immediately mentioned their vast amount of unused papers and gave me some of them that I can able to carry with me. This was a very strange experience for me because I did not expect such a thing. These paper are used inside of the notebooks as a page.

\textbf{The banner} (Figure \ref{fig:Banner_1}) is carried at graduation ceremony of Middle East Technical University in 2011 by the new Computer Engineering graduates. In Middle East Technical University there is a tradition that in graduation ceremony new grads walk through in the stadium and greet to the tribunes. With this event they carry some banners to express their feelings and point out the issues of the country in an ironic and humorous way. This one of them. At that time there are serious debates about freedom on the web. Most of the website are banned from the decision to the courts and they were not accessible. The slogan (Access to this banner is blocked by a court decision) decided by the new grads and before the ceremony I printed out the slogan to carried out as many people as it can and easy to readable from the people who seat at the tribunes.After the ceremony I could not throw away this banner. I do not know what to do it. It is a very big roll of paper to save but I could not throw away. I think that I will figure out later. Maybe I can use it as a draft paper. However is it worth to cut out this all long banner? Moreover to strengthen the banner we tape it from its boundaries. In other words some of the areas can not appropriate for writing. When I decided to my thesis subject I remembered to this banner. It stands in a corner in a dusty way. Now it is time to use it. It waited very log time and it is time to revive. I cut out them to the smaller pieces to use them as pages of notebooks. All pages have unique patterns. They contain parts of letters. Most of the time it is not recognizable belongs to which letter. These papers offers unique writing experience to the writer because of the patterns of letters and residue of tapes.

@@

Most of the materials that I collect are mass produced items. Generally their usage fall into the two category; education and food industry. They are found on public places. They are not personal objects like in the work of Tracey Emin’s \quotes{My Bed} even if it can be claimed that the collected papers from the laboratory contains personal travel tickets. Identity of owner are not certain.

@@

There are different dimensions of notebooks. Most of them are half of A4 (210mm x 297mm) or quarter of it. Collected papers dimensions shape the size of the notebooks.

@@

\textbf{Reunion.} These notebook’s pages are collected from restaurant Varuna Gezgin, in Ankara. We went there to meet some friends after long time. One of them was coming from Australia, the other one was coming from Norway. They were my friends from the university. We united again at this restaurant. The place has also similar story. Their founders and workers travel around the world. It is a popular restaurant of travelers. The decoration of that place contains a lot of items collected from different sides of the world. The concept of the place and our meeting perfectly matched. Same exist for the papers actually, they are separated from big paper rolls in the factory and by the action making notebooks they are also reunited again. These notebooks represent my memory about the place.

\textbf{Secondhand.} It can be thought that these notebooks are second hand objects. Used by someone else and still appropriate for reusing. Here I wish that these papers and notebooks are used more than twice.

\textbf{Daro.} For some of the notebooks it is not obvious to name them. At this point approach of Kurt Schwitters provides me a way. He generated his frequently used word \quotes{Merz} from an advertisement. It is a nonsense word and used in most of his works. I followed what he did and generated a word from the papers that used inside of the notebooks. I use the word \quotes{Daro} extracted from \quotes{Vardaroma Dondurmacısı} for the ones whose story are not obvious and significant.

@@

%
%
\subsection{Website}
Finding a new place to the discarded items is one of the main purposes of this project. Not only it finds a place in people’s life again, but also it finds another place in the digital space.

@@

%SketchBook Project is also inspired me a lot especially in terms of website. This project provides a platform to people in order to share their works with other people. It contains lots of works from all over the world. Full of creativity and showcase of richness of people’s expressions on the small notebooks. My work can be considered as a sketch book project through trash. Sketches or only creative progress is not the only consideration. You can send your lecture notes.

### 2016-01-17 chapter5_final.tex
turnitin fixes
Former-commit-id: c4e9dd913032a23d4355c7f057bba5be233580f1

This thesis takes a rather different approach to the discarded objects. It looks to philosophical ideas, theories and people's experiences of things in throw away culture.

People's evaluations of what is trash and treasure are both content and context dependent and are not fixed values. The line between them are blurred in the explored practices and works of art. Indeed, temporal value judgements of 'rubbish' and 'art' are often at the core of such art works. The analysis of selected works methodologies and approaches show that trash is fluid, and value indeterminate, and are often determined by context and personal subjectivities.

@@

>>>>

This thesis takes a rather different approach to the discarded objects. It looks to philosophical ideas, theories and people’s experiences of things in throw away culture.

People’s evaluations of what is trash and treasure are both content and context dependent and are not fixed values. The line between them are blurred in the explored practices and works of art. Indeed, temporal value judgements of ’rubbish’ and ’art’ are often at the core of such art works. The analysis of selected works methodologies and approaches show that trash is fluid, and value indeterminate, and are often determined by context and personal subjectivities.

@@

% Bunu landfill orchestrada kullan
% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%\summary{Ironic}
%\comment{IRONIC, maybe added to results of transformation, reusing trashed items in different contexts.} This misuse the detritus of the industrial age has been described by western theorist as ironic. the irony is often embodied visually and conceptually. opposite of natural use, expected perception. for example making something from nothing or turning trash into treasure. By juxtaposing different materials changing context and place.

% TODO From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
%Recycling has always been a common practice in the arts at least at a non-material level. From creating a world of words in literature, to rhythm and images in poetry, sampling in hip hop music, representation in the visual arts, or editing the illusory continuity of a film, art implies taking disparate elements (ideas, images, references, objects, etc.) and putting them together to form a new whole. Take and put. De-contextualize and re-contextualize. In that sense, art, as a system, is an act of recycling [from PAOLA IBARRA].

% TODO new comer
% FROM Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap
%\summary{Resistance} 
%\comment{Resistance, tactile, agnes varda?} If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins’s assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experience and they can do so only according to their own principles of existence. (sahlins 1992, 16)"

% TODO MOVE TO COMMON APPROACH, introduction.
%\comment{Semiotic Context, juxtapositions} \paraphrase{"In popular writing (such as novels), in television, films, music, and other forms of mass expression, the term trash is used to signify work that is of especially low value." \cite{lukas2012garbage}}

%"Garbage art (alternatively known as trash art or recycled art) is art created from materials including post-consumer and other waste, collected debris, or objects previously used for other purposes." "Creating art from garbage involves transforming the meaning of objects by placing them in new, aestheticized contexts. This practice is not new; tribal peoples have adapted bits of trash from industrialized societies into their traditional arts since coming into contact with products of the developed world." "Creating art from trash involves “consuming” garbage in the sense that artists appropriate and rearrange the materials in personal ways, transform their meanings, utilize them to their own ends, and represent them in new ways.It involves taking unwanted materials out of their “waste” context and recontextualizing them as “art.”" \cite{tauxe2012encyclopedia}

%\item Instead of a world that produce trash, how could it be a world created from trash?
